---
title: "Mixing data and text"
subtitle: "#TidyTuesday, 2019-12-02: 'Philly Parking Tickets' dataset."
author: "@jmcastagnetto, Jesus M. Castagnetto"
date: "`r Sys.Date()`"
output: 
  html_document:
    css: wider.css
---

```{r include = FALSE}
library(tidyverse)
library(datalegreyar)

load(here::here(
  "2019-12-03_philadelphia-parking-violations",
  "philly-data.Rdata")
)
```

## Motivation

Inspired by the [Emil's ](https://twitter.com/Emil_Hvitfeldt) [post](https://www.hvitfeldt.me/pkgcal2019/1/) about [datalegreyar](https://github.com/emitanaka/datalegreyar), I tried to combine text and data, within the limitations of the [datalegreya font](https://www.figs-lab.com/en/projects/datalegreya#header) ([repo at github](https://github.com/figs-lab/datalegreya)), and exploring the amount fined per day for each month day, trying to use a text with 31 characters (including spaces), and the amount for each day of the year, using a text with 365 characters (I cheated and included multiple spaces :-)

## Exploring the total amount fined per day of the month

```{r echo=FALSE}
df2 <- ph_df %>%
  mutate(
    day = lubridate::day(issue_datetime)
  ) %>%
  group_by(day) %>%
  summarise(
    total_fines = sum(fine, na.rm = TRUE)
  ) %>%
  arrange(day)

values <- df2$total_fines

toMUSD <- function(x) {
  sprintf("$%.1fM", x / 1e6)
}

dtxt <- datafy(values,
               text = "Monthly tickets in Philadelphia",
               start_value = 2,
               ignore_space = FALSE)

fig(dtxt,  
    start_value = 2,
    xlabs = c("first", "last"),
    color = "blue",
    type = "gradient",
    size = 90)
```

```{r echo=FALSE, fig.width=12, fig.height=2}
ggplot(df2, aes(x = sprintf("%02d", day), 
                y = total_fines, group = 1)) +
  geom_line() +
  labs(
    y = "",
    x = "Day of the month",
    caption = "@jmcastagnetto, Jesus M. Castagnetto"
  ) +
  scale_y_continuous(
    labels = scales::dollar,
    limits = c(1e6, 2.5e6), 
    minor_breaks = seq(1, 2.5, .1) * 1e6
  ) +
  theme_minimal(16) +
  theme(
    axis.title = element_text(hjust = 1)
  )
```

-----

## Looking at the amount fined per day of the year (2017)

```{r echo=FALSE}
df3 <- ph_df %>%
  mutate(
    date = lubridate::date(issue_datetime)
  ) %>%
  group_by(date) %>%
  summarise(
    total_fines = sum(fine, na.rm = TRUE)
  ) %>%
  arrange(date)

txt = "In the year 2017 in Philadelphia there were over one million two hundred and sixty thousand parking tickets   The total amount of those tickets was over fifty seven million two hundred and fifty eight thousand USD   And the agencies issuing the highest amounts were the Police and the Pensylvannia Parking Authority   The most common infraction was  Meter Expired  "

values <- df3$total_fines

dtxt <- datafy(values,
               text = txt,
               ignore_space = FALSE)

fig(dtxt,  
    start_value = 1,
    xlabs = c("jan01", "dic31"),
    color = "brown",
    size = 40)
```


```{r echo=FALSE, fig.width=12, fig.height=2}
ggplot(df3, aes(x = date, 
                y = total_fines, group = 1)) +
  geom_line() +
  labs(
    y = "",
    x = "",
    caption = "@jmcastagnetto, Jesus M. Castagnetto"
  ) +
  scale_y_continuous(
    labels = scales::dollar
  ) +
  theme_minimal(16) +
  theme(
    axis.title = element_text(hjust = 1)
  )
```


